### 2022-05-24 main/chapter_2ljets.tex
fix gtrsim; other tweaks

The benefit of an additional trigger could be increased signal yields, if that
trigger do not also harmfully increase inseparable backgrounds.
A study, \textit{which was performed by Knut Vadla}, compared the efficiencies
of including one-lepton triggers.
In a signal-region-like selection requiring two leptons, two jets and
$\met > 200~\eV[G]$, this study showed that two-lepton triggers already accept
in excess of $90\%$ of events from benchmark C1N2 models.
Therefore any additional trigger can therefore have at most a $\approx10\%$;
improvement, and adding one-lepton triggers was found to increase efficiency by
only a few percentage points, depending on the model.
We considered that to be too little.

Costs of triggers are attributable to human effort; adding triggers requires
software work to include them and their associated Monte Carlo weights, along
with additional studies to validation of background estimates and evaluation of
systematic uncertainties.
Similarly, our implementation of the Matrix Method fake/non-prompt lepton
background estimate (see Section~\ref{sec:2ljets_mm_fakes}) is not equipped to
handle one-lepton triggers.

Although jet and $\met$ triggers were not studied in detail, they require
hard objects, such as $\ptjone \gtrsim 400~\eV[G]$ or
$\met \gtrsim 100~\eV[G]$~\cite{atlas_twiki_lowest_unprescaled}.
Leptons are striking signals which \atlas\ can trigger on with much softer
requirements; lepton triggers allow us to use softer jets and $\met$,
which are relied upon throughout the $\twoljets$ analyses.

>>>>

The benefit of an additional trigger could be increased signal yields, if that
trigger do not also harmfully increase inseparable backgrounds.
A study, \textit{which was performed by Knut Vadla}, compared the efficiencies
of including one-lepton triggers.
In a signal-region-like selection requiring two leptons, two jets and
$\met > 200~\eV[G]$, this study showed that two-lepton triggers already accept
in excess of $90\%$ of events from benchmark C1N2 models.

Therefore, any additional trigger has at most a $\approx10\%$;
improvement. Adding one-lepton triggers was found to increase efficiency by
only a few percentage points, depending on the model.
We considered that to be too little.

Costs of triggers are attributable to human effort;
software work to include them and their associated Monte Carlo weights, along
with studies to validate background estimates and evaluate systematic
uncertainties.
Similarly, our implementation of the Matrix Method fake/non-prompt lepton
background estimate (see Section~\ref{sec:2ljets_mm_fakes}) is not equipped to
handle one-lepton triggers.

Although jet and $\met$ triggers were not studied in detail, they require
hard objects: examples are approximately $\ptjone > 400~\eV[G]$,
$p_\mathrm{T}^{\,j_3} > 200~\eV[G]$, or
$\met > 100~\eV[G]$~\cite{atlas_twiki_lowest_unprescaled}.
Leptons are striking signals which \atlas\ can trigger on with much softer
requirements; lepton triggers allow us to use softer jets and $\met$,
which are relied upon throughout the $\twoljets$ analyses.
